---
title: "tests"
author: "NEZZARI Abdelhak"
date: "January 1, 2020"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(tidytext)
library(textclean)
library(textdata)
library(topicmodels)
library(genius)

```

Retrieve the songs:

```{r}
christmas_songs <- readRDS(file="christmas_songs.rds")
if(!(christmas_songs %>% is.data.frame()))
{
  tuesdata <- tidytuesdayR::tt_load(2019, week = 52)
  christmas_songs <- tuesdata$christmas_songs
  rm(tuesdata)
  christmas_songs %>% saveRDS(file="christmas_songs.rds")
}
```

Retrieve the lyric of songs:
```{r }
lyric_df <- readRDS(file="lyric_df.rds")
if(!(lyric_df %>% is.data.frame()))
{
  lyric_df <- christmas_songs %>% 
    select("title" = song,
           "artist" = performer,
           songid,
           weekid) %>% 
    add_genius(artist = artist, title = title) %>% 
    select(-lyrics)
}


```

some songs are missing lyrics, find the songs missing lyrics:
```{r  }

 missing_lyrics_songs <-  christmas_songs %>% 
  anti_join(lyric_df,by = c("weekid", "songid")) %>% 
  rename(artist= performer )

```


The songs are missing their lyrics because they have wrong URLs:
```{r }

missing_lyrics_songs <- missing_lyrics_songs  %>% 
  mutate( songid = songid  %>% as.character(),
          artist = artist %>% as.character(),
          song   = str_remove(songid,artist ),
          url    = gen_song_url(artist = artist, song = song) )  
```

Retrieve now the lyrics with the right URLs of songs
```{r }
get_missing_lyrics <- function( raw) {
    tryCatch(
      raw["url"] %>% as.character() %>% genius_url() %>% 
        mutate(
        url=raw["url"],
        song=raw["song"],
        instance=raw["instance"] %>% as.double(),
        weeks_on_chart=raw["weeks_on_chart"] %>% as.double(),
        day=raw["day"] %>% as.double(),
        weekid = raw["weekid"],
        artist = raw["artist"],
        previous_week_position=raw["previous_week_position"] %>% as.double(),
        year   = raw["year"] %>% as.double(),
        week_position   = raw["week_position"] %>% as.double(),
        songid = raw["songid"],
        peak_position=raw["peak_position"] %>% as.double(),
        month=raw["month"] %>% as.double()),
      
      
        warning = function(warning) {print(paste("warning:",warning));
             list(track_title="",line=1,lyric="", songid="TOBEREMOVED", weekid="NA")},
          error   = function(error)   {print(paste("error:", error));
            list(track_title="",line=1,lyric="NA", songid="TOBEREMOVED", weekid="")}) 
}

missing_lyrics <- readRDS(file="missing_lyrics.rds")
if(!(missing_lyrics %>% is.data.frame()))
{
  missing_lyrics <- missing_lyrics_songs %>% 
    apply(1,get_missing_lyrics) %>% 
    bind_rows() %>% 
     filter(songid!="TOBEREMOVED")
  
  missing_lyrics %>% saveRDS(file="missing_lyrics.rds")
}
```


Collect the new calculated lyrics to lyric_df:
```{r}
if(!(lyric_df %>% is.data.frame()))
{ 
lyric_df <- lyric_df %>% bind_rows(
    missing_lyrics_songs %>% inner_join(missing_lyrics %>% select(lyric,line,track_title,songid,artist), by=c("songid","artist")) )

lyric_df %>% saveRDS( file = "lyric_df.rds")
}
```




Find if there are still missing lyrics:
```{r}
 missing_lyrics_songs <-  missing_lyrics_songs %>% anti_join(lyric_df)

missing_lyrics_songs %>% select(songid) %>% distinct() %>% nrow()
```




## Including Plots

You can also embed plots, for example:


```{r}

christmas_songs %>% group_by( year) %>% summarise( peak = mean(peak_position), 
                                                   chart = mean(weeks_on_chart) ) %>% tail()



christmas_songs %>% group_by( performer) %>% 
  summarise( peak = sum(peak_position), 
            chart = sum(weeks_on_chart),
             number_songs = n_distinct(songid) ) %>% 
  arrange( desc(peak), desc(chart)) %>%  
  top_n(6) %>% 
  ggplot(aes(performer, chart,color = peak)) + geom_point() 


```


```{r }
christmas_songs %>% group_by( performer) %>% 
  summarise( peak = sum(peak_position), 
            chart = sum(weeks_on_chart),
             number_songs = n_distinct(songid) ) %>% 
  arrange( desc(peak), desc(chart)) %>%  
  top_n(6) %>% 
  ggplot(aes(performer, chart,color = peak)) + geom_point() 


```



```{r }

christmas_songs %>% group_by( year) %>% 
  summarise( peak = sum(peak_position), 
            chart = sum(weeks_on_chart),
            number_songs = n_distinct(songid) ) %>% 
     ggplot( aes(year,peak)) + 
     geom_col(fill="blue")

```


```{r }
christmas_songs %>% group_by( year) %>% 
  summarise( "Highest position" = sum(peak_position), 
            "Number of weeks on billboard charts" = sum(weeks_on_chart),
            "Number of songs" = n_distinct(songid) ) %>% 
          gather(key= "key", value="value",-year) %>% 
     ggplot( ) + geom_bar( aes(year,value,fill=key),stat = "identity") +
  coord_flip() 
     

```


```{r }
christmas_songs %>% 
  group_by( year) %>% 
  summarise( "Peaks position" = sum(peak_position),  
             "Weeks on chart" = sum(weeks_on_chart), 
             "Number of songs" = n_distinct(songid) ) %>% 
   gather(key="Variable",value="value",-year) %>% 
   ggplot(aes(year,value,width=1)) +
   geom_tile(aes(fill=Variable))








```



```{r}
christmas_songs %>% group_by( year) %>% 
  summarise( "Highest position" = sum(peak_position), 
            "Number of weeks on billboard charts" = sum(weeks_on_chart),
            "Number of songs" = n_distinct(songid) ) %>% 
          gather(key= "Variable", value="value",-year) %>% 
     ggplot( ) + geom_bar( aes(year,value,fill=Variable),stat = "identity")+
     facet_wrap(~Variable) +
     theme(legend.position= "top" )+
      coord_flip() 
  

```


```{r }
data(stop_words)


lyric_df %>% 
  mutate( lyric = replace_contraction(lyric)) %>%  
  unnest_tokens(word,lyric) %>%  
  anti_join( stop_words ) %>% 
  mutate(word = textstem::lemmatize_words(word)) %>%
  count(track_title,word) %>% 
  cast_dtm(track_title,word,n) %>%
  LDA(k=7) %>% 
  tidy(matrix="gamma") %>% 
  rename(track_title = document) %>% 
  mutate(topic = paste("topic",topic,sep = "")) %>% 
  right_join((lyric_df %>% select(songid,track_title))) %>% 
  group_by(track_title,songid,gamma,topic) %>% 
  summarise( topic_count = n()) %>%
  spread(key = topic,value = topic_count , fill=0) %>%
  group_by(songid) %>% 
  summarise( topic1 = sum(topic1), 
             topic2 = sum(topic2),
             topic3 = sum(topic3), 
             topic4 = sum(topic4),
             topic5 = sum(topic5), 
             topic6 = sum(topic6),
             topic7 = sum(topic7), 
             gamma  = sum(gamma)) %>% 
  gather(key = "topic", value = "value", -songid) %>% 
  arrange(value) %>% 
  ggplot() +
  geom_bar(aes(songid,value,fill=topic), stat="identity",
           position = position_stack(reverse = TRUE)) +
  coord_flip() +
  theme(legend.position = "top")

```




```{r }
data(stop_words)


lyric_df %>% 
  mutate( lyric = replace_contraction(lyric)) %>%  
  unnest_tokens(word,lyric) %>%  
  anti_join( stop_words ) %>% 
  mutate(word = textstem::lemmatize_words(word)) %>%
  count(track_title,word) %>% 
  cast_dtm(track_title,word,n) %>%
  LDA(k=7) %>% 
  tidy(matrix="gamma") %>% 
  rename(track_title = document) %>% 
  mutate(topic = paste("topic",topic,sep = "")) %>% 
  right_join((lyric_df %>% select(year,track_title))) %>% 
  group_by(track_title,year,gamma,topic) %>% 
  summarise( topic_count = n()) %>%
  spread(key = topic,value = topic_count , fill=0) %>%
  group_by(year) %>% 
  summarise( topic1 = sum(topic1), 
             topic2 = sum(topic2),
             topic3 = sum(topic3), 
             topic4 = sum(topic4),
             topic5 = sum(topic5), 
             topic6 = sum(topic6),
             topic7 = sum(topic7), 
             gamma  = sum(gamma)) %>%
  gather(key = "topic", value = "value", -year) %>% 
  arrange(value) %>% 
  ggplot() +
  geom_bar(aes(year,value,fill=topic), stat="identity",
           position = position_stack(reverse = TRUE)) +
  coord_flip() +
  theme(legend.position = "top")

```

```{r }
lyric_df %>% 
  mutate( lyric = replace_contraction(lyric)) %>%  
  unnest_tokens(word,lyric) %>%  
  anti_join( stop_words ) %>% 
  mutate(word = textstem::lemmatize_words(word)) %>%
  count(track_title,word) %>% 
  cast_dtm(track_title,word,n) %>%
  LDA(k=7) %>% 
  tidy(matrix="gamma") %>% 
  rename(track_title = document) %>% 
  mutate(topic = paste("topic",topic,sep = "")) %>% 
  right_join((lyric_df %>% select(songid,track_title))) %>% 
  group_by(track_title,songid,gamma,topic) %>% 
  summarise( topic_count = n()) %>%
  spread(key = topic,value = topic_count , fill=0) %>%
  group_by(songid) %>% 
  summarise( topic1 = sum(topic1), 
             topic2 = sum(topic2),
             topic3 = sum(topic3), 
             topic4 = sum(topic4),
             topic5 = sum(topic5), 
             topic6 = sum(topic6),
             topic7 = sum(topic7), 
             gamma  = sum(gamma)) %>% 
  gather(key = "topic", value = "value", -songid) %>% 
  ggplot() +
  geom_bar(aes(songid,value,fill=topic),stat="identity", 
           position = position_stack(reverse = TRUE)) +
  coord_flip() +
  theme(legend.position = "top")

```


```{r }
data(stop_words)

lyric_df %>% 
  mutate( lyric = replace_contraction(lyric)) %>%  
  unnest_tokens(word,lyric) %>%  
  anti_join( stop_words ) %>% 
  mutate(word = textstem::lemmatize_words(word)) %>%
  left_join(get_sentiments("nrc"))   %>% 
  count(year,sentiment,word) %>%  
  spread(key = sentiment,value =n ,fill = 0) %>% 
  group_by(year) %>% 
  summarise(anger = sum(anger), 
            anticipation = sum(anticipation), 
            disgust = sum(disgust), 
            fear = sum(fear),
            joy = sum(joy), 
            negative = sum(negative), 
            positive = sum(positive), 
            sadness= sum(sadness), 
            surprise = sum(surprise), 
            trust = sum(trust)) %>% 
  gather(key = "sentiment", value = "value", -year) %>% 
  ggplot() +
  geom_bar(aes(year,value,fill=sentiment),stat="identity", position = position_stack(reverse = TRUE)) +
  coord_flip() +
  theme(legend.position = "top")
```

```{r}
data(stop_words)

lyric_df %>% 
  mutate( lyric = replace_contraction(lyric)) %>%  
  unnest_tokens(word,lyric) %>%  
  anti_join( stop_words ) %>% 
  mutate(word = textstem::lemmatize_words(word)) %>%
  left_join(get_sentiments("nrc"))   %>% 
  count(songid,sentiment,word) %>%  
  spread(key = sentiment,value =n ,fill = 0) %>% 
  group_by(songid) %>% 
  summarise(anger = sum(anger), 
            anticipation = sum(anticipation), 
            disgust = sum(disgust), 
            fear = sum(fear),
            joy = sum(joy), 
            negative = sum(negative), 
            positive = sum(positive), 
            sadness= sum(sadness), 
            surprise = sum(surprise), 
            trust = sum(trust)) %>%
  arrange(anger,anticipation,fear,joy,surprise,trust,negative,sadness,positive) %>% 
  head(20) %>% 
  gather(key = "sentiment", value = "value", -songid) %>% 
  ggplot() +
  geom_bar(aes(songid,value,fill=sentiment),stat="identity", position = position_stack(reverse = TRUE)) +
  coord_flip() +
  theme(legend.position = "top")








```



```{r}
data(stop_words)


lyric_df %>% 
  mutate( lyric = replace_contraction(lyric)) %>%
  unnest_tokens(word,lyric) %>%  
  anti_join( stop_words ) %>% 
  mutate(word = textstem::lemmatize_words(word)) %>%
  left_join(get_sentiments("nrc"))   %>% 
  count(songid,peak_position,sentiment,word) %>%
  spread(key = sentiment,value =n ,fill = 0) %>% 
  group_by(songid) %>% 
  summarise(anger = sum(anger), 
            anticipation = sum(anticipation), 
            disgust = sum(disgust), 
            fear = sum(fear),
            joy = sum(joy), 
            negative = sum(negative), 
            positive = sum(positive), 
            sadness= sum(sadness), 
            surprise = sum(surprise), 
            trust = sum(trust),
            peak_position = mean(peak_position)) %>%
  arrange(peak_position) %>% 
  head(20) %>% 
  gather(key = "sentiment", value = "value", -songid) %>% 
  ggplot() +
  geom_bar(aes(songid,value,fill=sentiment),stat="identity", position = position_stack(reverse = TRUE)) +
  coord_flip() +
  theme(legend.position = "top")
```


```{r}
 coord_radar <- function (theta = "x", start = 0, direction = 1) 
 {
   theta <- match.arg(theta, c("x", "y"))
   r <- if (theta == "x") 
     "y"
   else "x"
   ggproto("CordRadar", CoordPolar, theta = theta, r = r, start = start, 
           direction = sign(direction),
           is_linear = function(coord) TRUE)
 } 

```



```{r}
data(stop_words)


lyric_df %>% 
  mutate( lyric = replace_contraction(lyric)) %>%
  unnest_tokens(word,lyric) %>%  
  anti_join( stop_words ) %>% 
  mutate(word = textstem::lemmatize_words(word)) %>%
  left_join(get_sentiments("nrc"))   %>% 
  count(songid,week_position,sentiment,word) %>%
  spread(key = sentiment,value =n ,fill = 0) %>% 
  group_by(songid) %>% 
  summarise(anger = sum(anger), 
            anticipation = sum(anticipation), 
            disgust = sum(disgust), 
            fear = sum(fear),
            joy = sum(joy), 
            negative = sum(negative), 
            positive = sum(positive), 
            sadness= sum(sadness), 
            surprise = sum(surprise), 
            trust = sum(trust),
            week_position = mean(week_position)) %>%
  
  arrange(week_position) %>% 
  select(songid,anger,sadness,fear,surprise,anticipation,trust) %>%
  head(4) %>% 
  gather(key = "sentiment", value = "value", -songid) %>% 
  ggplot(aes(x=sentiment,y=value)) +
  geom_polygon(aes(group = songid, color = songid), fill = NA,  show.legend = FALSE) +
  geom_line(aes(group = songid, color = songid)) +
   theme(strip.text.x = element_text(size = rel(0.8)),
         axis.text.x = element_text(size = rel(0.8)),
         axis.ticks.y = element_blank(),
         axis.text.y = element_blank()) +
   xlab("") + ylab("") +
   coord_radar()
```

```{r}
lyric_df %>% mutate(year=as.factor(year)) %>% 
  mutate( lyric = replace_contraction(lyric)) %>%
  unnest_tokens(word,lyric) %>%  
  anti_join( stop_words ) %>% 
  mutate(word = textstem::lemmatize_words(word)) %>%
  left_join(get_sentiments("nrc"))   %>% 
  count(year,week_position,sentiment,word) %>%
  spread(key = sentiment,value =n ,fill = 0) %>% 
  group_by(year) %>% 
  summarise(anger = sum(anger), 
            anticipation = sum(anticipation), 
            disgust = sum(disgust), 
            fear = sum(fear),
            joy = sum(joy), 
            negative = sum(negative), 
            positive = sum(positive), 
            sadness= sum(sadness), 
            surprise = sum(surprise), 
            trust = sum(trust),
            week_position = mean(week_position)) %>%
  arrange(desc(week_position) )%>% 
  select(year,surprise,trust,joy,positive,sadness) %>%
  head(10) %>% 
  gather(key = "sentiment", value = "value", -year) %>% 
  ggplot(aes(x=sentiment,y=value)) +
  geom_polygon(aes(group = year, color = year), fill = NA,  show.legend = FALSE) +
  geom_line(aes(group = year, color = year)) +
   theme(strip.text.x = element_text(size = rel(0.8)),
         axis.text.x = element_text(size = rel(0.8)),
         axis.ticks.y = element_blank(),
         axis.text.y = element_blank()) +
   xlab("") + ylab("") +
   coord_radar()
```





Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
